Taking Linear Logic Apart

### 2018-04-25 doc/tlla2018/main.tex
Finished edits of introduction & related work

\section{Classical Processes}

@@

\section{Hypersequent Classical Processes}

@@

\section{Relation between \cp and \hcp}

>>>>

We proceed as follows.
We introduce \cp and restate its proofs of subject reduction and progress
(\cref{sec:cp}), then introduce \hcp and give its proofs of subject reduction
and progress (\cref{sec:hcp}).
We then prove several properties relating the two. Specifically, we prove that
every \cp process is an \hcp process, that every \hcp process corresponds to
several entangled \cp processes, and that \hcp supports the same communication
protocols as \cp, and no more (\cref{sec:cp2hcp}).
Finally, we discuss related work and conclude
(\cref{sec:related-work,sec:conclusions}).

\section{Classical Processes}
\label{sec:cp}

@@

\section{Hypersequent Classical Processes}
\label{sec:hcp}

@@

\section{Relation between \cp and \hcp}
\label{sec:cp2hcp}
